Article Name

### 2022-06-21 elsevier/manuscript.Rmd
`options(scipen=999)`: displaying `20000` instead of `2 x 10^4`
`!` update `manuscript`: add syntax before the output

library(here)
library(tidyverse)
library(kableExtra)
```

@@

# Introduction {#intro}
1. general information
1. research gap
1. research aim

@@

@@

If the caption is too long (fig.\ref{fig:2021}), use the [text-reference](https://bookdown.org/yihui/rmarkdown/bookdown-markdown.html#text-references). 
See the code in "elsevier/manuscript.Rmd" for more information.

@@

## Adding tables {#table}
```{r}
data %>% 
          group_by(supp) %>%
          summarise(median = median(len),
                    mean = mean(len)) %>% 
	kable("simple",
	      booktabs = T,
	      col.names = c("Supplement type", 
	      	    	"Median",
	      	    	"Mean"), 
	      align = "cll",
	      caption = "\\label{tab:cooltable}Mean and Median")
```

## Adding equation {#equation}
1. The _variable_ \(x\) and the __function__ \(f(x)\)
1. The *variable* $x$ and the **function** $f(x)$
1. superscript^2^
1. NO~2~, NO~3~, PO~4~, NH~4~

@@

or

@@

@@

1. Fig.\ref{fig:boxplot} and fig.\ref{fig:2021}
1. Table. \ref{tab:cooltable}
1. Equation \ref{eq:cutoff}
1. Section \ref{intro} and section \ref{figure}

## Citation syntax
- cite directly @Davis2009
- put citations in parentheses [@Walls2018]
- cite multiple entries [@Davis2009; @Walls2018]
- suppress the mention of the author [-@Liu2011a]

# Results {#result}
## Use code inline
The maximum tooth length is `r max(data$len)`.

@@

```
# References
<div id="refs"></div>
# Supplementary Materials
```
- check spelling in rmarkdown: `F7`
- [word count addin](https://github.com/benmarwick/wordcountaddin)

>>>>

library(here)
library(tidyverse)
library(kableExtra)

options(scipen = 999)
```

@@

# Introduction {#intro}

Setting __global options__ that apply to every chunk in the file.

````markdown
`r ''````{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(here)
library(tidyverse)
library(kableExtra)

# displaying 20000 instead of 2 x 10^4
options(scipen = 999)
```
````

````markdown
`r ''````{r}
# import data
data <- read_csv(here("data", "process", "newdata.csv"))
```
````

Ordered list items:

```markdown
1. general information
1. research gap
1. research aim
```

The output is:

1. general information
1. research gap
1. research aim

@@

````markdown
`r ''````{r boxplot, fig.cap='A boxplot', out.height="50%", fig.align='center'}
knitr::include_graphics(here::here("results", "figures", "boxplot.pdf"))
```
````

@@

If the caption is too long (Fig. \ref{fig:2021}), use [text-reference](https://bookdown.org/yihui/rmarkdown/bookdown-markdown.html#text-references).

`(ref:longcaption) This is a very long caption`

````markdown
`r ''````{r 2021, fig.cap='(ref:longcaption', out.width="50%", fig.align='center'}
knitr::include_graphics(here::here("results", "pictures", "2021.png"))
```
````

@@

## Adding tables {#table}

````markdown
`r ''````{r}
data %>% 
          group_by(supp) %>%
          summarise(median = median(len),
                    mean = mean(len)) %>% 
	kable("simple",
	      booktabs = T,
	      col.names = c("Supplement type", 
	      	    	"Median",
	      	    	"Mean"), 
	      align = "cll",
	      caption = "\\label{tab:cooltable}Mean and Median")
```
````

```{r}
data %>% 
          group_by(supp) %>%
          summarise(median = median(len),
                    mean = mean(len)) %>% 
	kable("simple",
	      booktabs = T,
	      col.names = c("Supplement type", 
	      	    	"Median",
	      	    	"Mean"), 
	      align = "cll",
	      caption = "\\label{tab:cooltable}Mean and Median")
```

## Adding equation {#equation}

```markdown
1. The _variable_ \(x\) and the __function__ \(f(x)\)
1. The *variable* $x$ and the **function** $f(x)$
1. superscript^2^
1. NO~2~, NO~3~, PO~4~, NH~4~
1. 25 µL
```

The output is:

1. The _variable_ \(x\) and the __function__ \(f(x)\)
1. The *variable* $x$ and the **function** $f(x)$
1. superscript^2^
1. NO~2~, NO~3~, PO~4~, NH~4~
1. 25 µL

Adding equations using the LaTeX syntax

```latex
\[Y|X \sim Bernoulli(p)\]
```

@@

```latex
\begin{equation}
\label{eq:cutoff}
p(x) = P(Y = 1|X = x) = 
\left\{
    \begin{array}{lr}
          p_1 = P(Y = 1|X \le cp), & \text{if } x \le cp\\
          p_2 = P(Y = 1|X > cp), & \text{if } x > cp
    \end{array}
\right.
\end{equation}
```

@@

```latex
\begin{subequations}
  \label{eq:model}
  \begin{align}
  \label{eq:modela}
P(y|\theta, \lambda) = 
\left\{
    \begin{array}{lr}
       \theta & \text{if } y = 0\\
       (1 - \theta) \frac{Poisson(y|\lambda)}{1 - PoissonCDF(0|\lambda)} 
       & \text{if } y > 0
    \end{array}
\right. \\
  \label{eq:modelb}
logit(\theta) = \alpha_0 + \alpha_1 * x_1 + \alpha_2 * x_2 \\
  \label{eq:modelc}
log(\lambda) = \beta_0 + \beta_1 * x_1 + \beta_2 * x_2 + \nu
  \end{align}
\end{subequations}
```

\begin{subequations}
  \label{eq:model}
  \begin{align}
  \label{eq:modela}
P(y|\theta, \lambda) = 
\left\{
    \begin{array}{lr}
          \theta & \text{if } y = 0\\
          (1 - \theta) \frac{Poisson(y|\lambda)}{1 - PoissonCDF(0|\lambda)} 
          & \text{if } y > 0
    \end{array}
\right. \\
  \label{eq:modelb}
logit(\theta) = \alpha_0 + \alpha_1 * x_1 + \alpha_2 * x_2 \\
  \label{eq:modelc}
log(\lambda) = \beta_0 + \beta_1 * x_1 + \beta_2 * x_2 + \nu
  \end{align}
\end{subequations}

@@

```markdown
1. Fig.\ref{fig:boxplot} and fig.\ref{fig:2021}
1. Table. \ref{tab:cooltable}
1. Equation \ref{eq:cutoff}, Eq. \ref{eq:model}, Eq. \ref{eq:modela}
1. Section \ref{intro} and section \ref{figure}
```

The output is:

1. Fig. \ref{fig:boxplot} and Fig. \ref{fig:2021}
1. Table. \ref{tab:cooltable}
1. Equation \ref{eq:cutoff}, Eq. \ref{eq:model}, Eq. \ref{eq:modela}
1. Section \ref{intro} and section \ref{figure}

## Citation syntax
- `@Davis2009`: cite directly @Davis2009
- `[@Walls2018]`: put citations in parentheses [@Walls2018]
- `[@Davis2009; @Walls2018]`: cite multiple entries [@Davis2009; @Walls2018]
- `[-@Liu2011a]`: suppress the mention of the author [-@Liu2011a]

# Results {#result}
## Use code inline

```markdown
The maximum tooth length is `r '\x60r max(data$len)\x60'`.
```

The maximum tooth length is `r max(data$len)`.

@@

```markdown
# References
<div id="refs"></div>
# Supplementary Materials
```

- check spelling in rmarkdown: `F7`
- [word count addin](https://github.com/benmarwick/wordcountaddin)

### 2022-06-21 elsevier/manuscript.tex
`options(scipen=999)`: displaying `20000` instead of `2 x 10^4`
`!` update `manuscript`: add syntax before the output

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Article Name},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% Pandoc header
%fix position of table, figure
\usepackage{float}
\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
    \expandafter\origfigure\expandafter[H]
} {
    \endorigfigure
}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

@@

@@

If the caption is too long (fig.\ref{fig:2021}), use the
\href{https://bookdown.org/yihui/rmarkdown/bookdown-markdown.html\#text-references}{text-reference}.
See the code in ``elsevier/manuscript.Rmd'' for more information.

@@

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The \emph{variable} \(x\) and the \textbf{function} \(f(x)\)
\item
  The \emph{variable} \(x\) and the \textbf{function} \(f(x)\)
\item
  superscript\textsuperscript{2}
\item
  NO\textsubscript{2}, NO\textsubscript{3}, PO\textsubscript{4},
  NH\textsubscript{4}
\end{enumerate}

@@

or

@@

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Fig.\ref{fig:boxplot} and fig.\ref{fig:2021}
\item
  Table. \ref{tab:cooltable}
\item
  Equation \ref{eq:cutoff}
\item
  Section \ref{intro} and section \ref{figure}
\end{enumerate}

@@

\begin{itemize}
\tightlist
\item
  cite directly Davis et al. (2009)
\item
  put citations in parentheses (Walls et al., 2018)
\item
  cite multiple entries (Davis et al., 2009; Walls et al., 2018)
\item
  suppress the mention of the author (2011)
\end{itemize}

@@

@@

\begin{verbatim}
# References
<div id="refs"></div>
# Supplementary Materials
\end{verbatim}

@@

\renewcommand{\thefigure}{S\arabic{figure}}

\setcounter{figure}{0} \renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0} \renewcommand{\theequation}{S\arabic{equation}}
\setcounter{equation}{0}

\section*{Supplementary materials}\label{appendix}
\addcontentsline{toc}{section}{Supplementary materials}

@@

@@

@@

@@

I am happy to submit my manuscript, \textbf{article\_name}, for your
consideration at \emph{journal\_name}. This work \emph{do sth
interesting}. The main conclusion is that \emph{sth cool}.

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Article Name},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% Pandoc header
% nullify the abstract environment
% \renewenvironment{abstract}{}{}

% Use the `align` environment inside the `subequations` environment 
% from the `amsmath` package to label equation with subnumber (e.g. 1a, 1b)
\usepackage{amsmath}

%fix position of table, figure
\usepackage{float}
\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
    \expandafter\origfigure\expandafter[H]
} {
    \endorigfigure
}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

Setting \textbf{global options} that apply to every chunk in the file.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{```\{r setup, include=FALSE\}}
\NormalTok{knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)}

\NormalTok{library(here)}
\NormalTok{library(tidyverse)}
\NormalTok{library(kableExtra)}

\FunctionTok{# displaying 20000 instead of 2 x 10^4}
\NormalTok{options(scipen = 999)}
\NormalTok{```}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{```\{r\}}
\FunctionTok{# import data}
\NormalTok{data <- read_csv(here("data", "process", "newdata.csv"))}
\NormalTok{```}
\end{Highlighting}
\end{Shaded}

Ordered list items:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{1. }\FloatTok{general information}
\FloatTok{1. research gap}
\FloatTok{1. research aim}
\end{Highlighting}
\end{Shaded}

The output is:

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{```\{r boxplot, fig.cap='A boxplot', out.height="50%", fig.align='center'\}}
\NormalTok{knitr::include_graphics(here::here("results", "figures", "boxplot.pdf"))}
\NormalTok{```}
\end{Highlighting}
\end{Shaded}

@@

If the caption is too long (Fig. \ref{fig:2021}), use
\href{https://bookdown.org/yihui/rmarkdown/bookdown-markdown.html\#text-references}{text-reference}.

\texttt{(ref:longcaption)\ This\ is\ a\ very\ long\ caption}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{```\{r 2021, fig.cap='(ref:longcaption', out.width="50%", fig.align='center'\}}
\NormalTok{knitr::include_graphics(here::here("results", "pictures", "2021.png"))}
\NormalTok{```}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{```\{r\}}
\NormalTok{data %>% }
\BaseNTok{          group_by(supp) %>%}
\BaseNTok{          summarise(median = median(len),}
\BaseNTok{                    mean = mean(len)) %>% }
\BaseNTok{    kable("simple",}
\BaseNTok{          booktabs = T,}
\BaseNTok{          col.names = c("Supplement type", }
\BaseNTok{                    "Median",}
\BaseNTok{                    "Mean"), }
\BaseNTok{          align = "cll",}
\BaseNTok{          caption = "\textbackslash{}\textbackslash{}label\{tab:cooltable\}Mean and Median")}
\NormalTok{```}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{1. }\FloatTok{The _variable_ \textbackslash{}(x\textbackslash{}) and the __function__ \textbackslash{}(f(x)\textbackslash{})}
\FloatTok{1. The *variable* $x$ and the **function** $f(x)$}
\FloatTok{1. superscript^2^}
\FloatTok{1. NO~2~, NO~3~, PO~4~, NH~4~}
\FloatTok{1. 25 µL}
\end{Highlighting}
\end{Shaded}

The output is:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The \emph{variable} \(x\) and the \textbf{function} \(f(x)\)
\item
  The \emph{variable} \(x\) and the \textbf{function} \(f(x)\)
\item
  superscript\textsuperscript{2}
\item
  NO\textsubscript{2}, NO\textsubscript{3}, PO\textsubscript{4},
  NH\textsubscript{4}
\item
  25 µL
\end{enumerate}

Adding equations using the LaTeX syntax

\begin{Shaded}
\begin{Highlighting}[]
\SpecialStringTok{\textbackslash{}[Y|X }\SpecialCharTok{\textbackslash{}sim}\SpecialStringTok{ Bernoulli(p)\textbackslash{}]}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{\textbackslash{}begin}\NormalTok{\{}\ExtensionTok{equation}\NormalTok{\}}
\SpecialCharTok{\textbackslash{}label}\SpecialStringTok{\{eq:cutoff\}}
\SpecialStringTok{p(x) = P(Y = 1|X = x) = }
\SpecialCharTok{\textbackslash{}left\textbackslash{}\{}
\SpecialStringTok{    }\KeywordTok{\textbackslash{}begin}\NormalTok{\{}\ExtensionTok{array}\NormalTok{\}}\SpecialStringTok{\{lr\}}
\SpecialStringTok{          p_1 = P(Y = 1|X }\SpecialCharTok{\textbackslash{}le}\SpecialStringTok{ cp), & }\SpecialCharTok{\textbackslash{}text}\NormalTok{\{if \}}\SpecialStringTok{ x }\SpecialCharTok{\textbackslash{}le}\SpecialStringTok{ cp}\SpecialCharTok{\textbackslash{}\textbackslash{}}
\SpecialStringTok{          p_2 = P(Y = 1|X > cp), & }\SpecialCharTok{\textbackslash{}text}\NormalTok{\{if \}}\SpecialStringTok{ x > cp}
\SpecialStringTok{    }\KeywordTok{\textbackslash{}end}\NormalTok{\{}\SpecialStringTok{array\}}
\SpecialCharTok{\textbackslash{}right}\SpecialStringTok{.}
\KeywordTok{\textbackslash{}end}\NormalTok{\{}\ExtensionTok{equation}\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{\textbackslash{}begin}\NormalTok{\{}\ExtensionTok{subequations}\NormalTok{\}}
  \KeywordTok{\textbackslash{}label}\NormalTok{\{}\ExtensionTok{eq:model}\NormalTok{\}}
  \KeywordTok{\textbackslash{}begin}\NormalTok{\{}\ExtensionTok{align}\NormalTok{\}}
\SpecialStringTok{  }\SpecialCharTok{\textbackslash{}label}\SpecialStringTok{\{eq:modela\}}
\SpecialStringTok{P(y|}\SpecialCharTok{\textbackslash{}theta}\SpecialStringTok{, }\SpecialCharTok{\textbackslash{}lambda}\SpecialStringTok{) = }
\SpecialCharTok{\textbackslash{}left\textbackslash{}\{}
\SpecialStringTok{    }\KeywordTok{\textbackslash{}begin}\NormalTok{\{}\ExtensionTok{array}\NormalTok{\}}\SpecialStringTok{\{lr\}}
\SpecialStringTok{       }\SpecialCharTok{\textbackslash{}theta}\SpecialStringTok{ & }\SpecialCharTok{\textbackslash{}text}\NormalTok{\{if \}}\SpecialStringTok{ y = 0}\SpecialCharTok{\textbackslash{}\textbackslash{}}
\SpecialStringTok{       (1 - }\SpecialCharTok{\textbackslash{}theta}\SpecialStringTok{) }\SpecialCharTok{\textbackslash{}frac}\SpecialStringTok{\{Poisson(y|}\SpecialCharTok{\textbackslash{}lambda}\SpecialStringTok{)\}\{1 - PoissonCDF(0|}\SpecialCharTok{\textbackslash{}lambda}\SpecialStringTok{)\} }
\SpecialStringTok{       & }\SpecialCharTok{\textbackslash{}text}\NormalTok{\{if \}}\SpecialStringTok{ y > 0}
\SpecialStringTok{    }\KeywordTok{\textbackslash{}end}\NormalTok{\{}\SpecialStringTok{array\}}
\SpecialCharTok{\textbackslash{}right}\SpecialStringTok{. }\SpecialCharTok{\textbackslash{}\textbackslash{}}
\SpecialStringTok{  }\SpecialCharTok{\textbackslash{}label}\SpecialStringTok{\{eq:modelb\}}
\SpecialStringTok{logit(}\SpecialCharTok{\textbackslash{}theta}\SpecialStringTok{) = }\SpecialCharTok{\textbackslash{}alpha}\SpecialStringTok{_0 + }\SpecialCharTok{\textbackslash{}alpha}\SpecialStringTok{_1 * x_1 + }\SpecialCharTok{\textbackslash{}alpha}\SpecialStringTok{_2 * x_2 }\SpecialCharTok{\textbackslash{}\textbackslash{}}
\SpecialStringTok{  }\SpecialCharTok{\textbackslash{}label}\SpecialStringTok{\{eq:modelc\}}
\SpecialStringTok{log(}\SpecialCharTok{\textbackslash{}lambda}\SpecialStringTok{) = }\SpecialCharTok{\textbackslash{}beta}\SpecialStringTok{_0 + }\SpecialCharTok{\textbackslash{}beta}\SpecialStringTok{_1 * x_1 + }\SpecialCharTok{\textbackslash{}beta}\SpecialStringTok{_2 * x_2 + }\SpecialCharTok{\textbackslash{}nu}
\SpecialStringTok{  }\KeywordTok{\textbackslash{}end}\NormalTok{\{}\ExtensionTok{align}\NormalTok{\}}
\KeywordTok{\textbackslash{}end}\NormalTok{\{}\ExtensionTok{subequations}\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{subequations}
  \label{eq:model}
  \begin{align}
  \label{eq:modela}
P(y|\theta, \lambda) = 
\left\{
    \begin{array}{lr}
          \theta & \text{if } y = 0\\
          (1 - \theta) \frac{Poisson(y|\lambda)}{1 - PoissonCDF(0|\lambda)} 
          & \text{if } y > 0
    \end{array}
\right. \\
  \label{eq:modelb}
logit(\theta) = \alpha_0 + \alpha_1 * x_1 + \alpha_2 * x_2 \\
  \label{eq:modelc}
log(\lambda) = \beta_0 + \beta_1 * x_1 + \beta_2 * x_2 + \nu
  \end{align}
\end{subequations}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{1. }\FloatTok{Fig.\textbackslash{}ref\{fig:boxplot\} and fig.\textbackslash{}ref\{fig:2021\}}
\FloatTok{1. Table. \textbackslash{}ref\{tab:cooltable\}}
\FloatTok{1. Equation \textbackslash{}ref\{eq:cutoff\}, Eq. \textbackslash{}ref\{eq:model\}, Eq. \textbackslash{}ref\{eq:modela\}}
\FloatTok{1. Section \textbackslash{}ref\{intro\} and section \textbackslash{}ref\{figure\}}
\end{Highlighting}
\end{Shaded}

The output is:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Fig. \ref{fig:boxplot} and Fig. \ref{fig:2021}
\item
  Table. \ref{tab:cooltable}
\item
  Equation \ref{eq:cutoff}, Eq. \ref{eq:model}, Eq. \ref{eq:modela}
\item
  Section \ref{intro} and section \ref{figure}
\end{enumerate}

@@

\begin{itemize}
\tightlist
\item
  \texttt{@Davis2009}: cite directly Davis et al. (2009)
\item
  \texttt{{[}@Walls2018{]}}: put citations in parentheses (Walls et al.,
  2018)
\item
  \texttt{{[}@Davis2009;\ @Walls2018{]}}: cite multiple entries (Davis
  et al., 2009; Walls et al., 2018)
\item
  \texttt{{[}-@Liu2011a{]}}: suppress the mention of the author (2011)
\end{itemize}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{The maximum tooth length is }\BaseNTok{`r max(data$len)`}\NormalTok{.}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{# References}
\NormalTok{<div id="refs"></div>}
\FunctionTok{# Supplementary Materials}
\end{Highlighting}
\end{Shaded}

@@

\appendix

\renewcommand{\thefigure}{A.\arabic{figure}}

\setcounter{figure}{0} \renewcommand{\thetable}{A.\arabic{table}}
\setcounter{table}{0} \renewcommand{\theequation}{A.\arabic{equation}}
\setcounter{equation}{0}

\section{Supplementary materials A}\label{appendixA}

\subsection{A cool figure}\label{a-cool-figure}

@@

\subsection{An awesome table}\label{an-awesome-table}

@@

\renewcommand{\thefigure}{B.\arabic{figure}}

\setcounter{figure}{0} \renewcommand{\thetable}{B.\arabic{table}}
\setcounter{table}{0} \renewcommand{\theequation}{B.\arabic{equation}}
\setcounter{equation}{0}

\section{Supplementary materials B}\label{appendixB}

\subsection{Some random code}\label{some-random-code}

@@

\subsection{A green photo}\label{a-green-photo}

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/LY/Google Drive/Git/writing_journal_article_in_rmarkdown/results/pictures/green}

\caption{A green photo}\label{fig:green}
\end{figure}

@@

I am happy to submit my manuscript, \textbf{article\_name}, for your
consideration at \emph{journal\_name}. This work \emph{did sth
interesting}. The main conclusion is that \emph{sth cool}.
